Multiple regression: TRELIS-Q WP5 data

### 2024-02-15 Rmd/bookchapter.TRELIS-Q-WP5.Rmd
Fixed analysis.

# jeg skulet Annet / ønsker ikke å oppgi, siden det bare er to personer
# skjuler som Kvinne, siden det er flest av de
data_clean$Gender[data_clean$Gender == "Annet/ønsker ikke å oppgi"] <- NA # "Kvinne"
#gender_r[is.na(gender_r)] <- 1
```

@@

```{r}
# ref https://www.datanovia.com/en/blog/top-r-color-palettes-to-know-for-great-data-visualization/#viridis-color-palettes
# https://www.statology.org/interaction-plot-r/
interaction.plot(x.factor = factor(data_clean$Trinn),
                 trace.factor = factor(data_clean$Gender),
                 response = data_clean$TK,
                 ylab = "TK",
                 xlab = "Target grade level",
                 col = viridis(2), # c("pink", "blue"), 
                 trace.label = "Gender")
```

```{r}
# https://www.statology.org/interaction-plot-r/
interaction.plot(x.factor = factor(data_clean$Trinn),
                 trace.factor = factor(data_clean$Gender),
                 response = data_clean$TPACK,
                 ylab = "TPACK",
                 xlab = "Target grade level",
                 col = viridis(2), # c("pink", "blue"),
                 trace.label = "Gender")
```

```{r}
interaction.plot(x.factor = factor(data_clean$semester), # label=c("Year 2/3", "Year 5")),
                 trace.factor = factor(data_clean$studiested), # label=c("institute 1", "institute 2", "institute 3", "institute 4", "institute 5")),
                 response = data_clean$TPACK,
                 ylab = "TPACK",
                 xlab = "Year of study",
                 col = viridis(5), # c("red", "green", "orange", "pink", "blue"),
                 trace.label = "Institute")
```

```{r}
interaction.plot(x.factor = factor(data_clean$Gender),
                 trace.factor = factor(data_clean$studiested), #label=c("institute 1", "institute 2", "institute 3", "institute 4", "institute 5")),
                 response = data_clean$TPACK,
                 ylab = "TPACK",
                 xlab = "Gender",
                 col = viridis(5), #c("red", "green", "orange", "pink", "blue"),
                 trace.label = "Institute")
```

@@

```{r level1}
# kovariater; we use scale to standardize when using interaction effects
# sjekk: er det riktig å skalere?
m1 <- lm_robust(scale(TPACK, center=T, scale=T) ~ factor(Gender) * factor(Trinn) * factor(semester), 
                clusters = factor(studiested), data=data_clean)
summary(m1)
```

```{r level2}
# studiested; HVL velges som referansekategori siden den har lavest TPACK-verdi av alle
m2 <- lm_robust(scale(TPACK) ~ factor(Gender) * factor(Trinn) * factor(semester) * factor(studiested), 
                clusters = factor(studiested), data=data_clean)
summary(m2)
```

@@

```{r PCK}
# PCK
m3 <- lm_robust(TPACK ~ factor(Gender) * factor(Trinn) * factor(semester) * factor(studiested) + PCK, 
                clusters = factor(studiested), data=data_clean)
summary(m3)

@@

```{r TK}
# TK
m4 <- lm_robust(TPACK ~ factor(Gender) * factor(Trinn) * factor(semester) * factor(studiested) + PCK + TK, 
                clusters = factor(studiested), data=data_clean)
summary(m4)

>>>>

# jeg skulet Annet / ønsker ikke å oppgi, siden det bare er to personer
# skjuler som Kvinne, siden det er flest av de
data_clean$Gender[data_clean$Gender == "Annet/ønsker ikke å oppgi"] <- NA # "Kvinne"
#gender_r[is.na(gender_r)] <- 1

# merge 2. and 3. year (Naturfag 1)
#data_clean$semester[data_clean$semester == "2. år"] <- "3. år"
```

@@

```{r TK_gender_trinn}
# ref https://www.datanovia.com/en/blog/top-r-color-palettes-to-know-for-great-data-visualization/#viridis-color-palettes
# https://www.statology.org/interaction-plot-r/
interaction.plot(x.factor = factor(data_clean$Trinn),
                 trace.factor = factor(data_clean$Gender),
                 response = data_clean$TK,
                 ylab = "TK",
                 xlab = "Target grade level",
                 col = viridis(2), # c("pink", "blue"), 
                 trace.label = "Gender")
```

Different signs on slope, a clear indication of interaction effects on TK from gender and target grade level.

### Level 1

```{r TPACK_gender_trinn}
# https://www.statology.org/interaction-plot-r/
interaction.plot(x.factor = factor(data_clean$Gender),
                 trace.factor = factor(data_clean$Trinn),
                 response = data_clean$TPACK,
                 type = "b",
                 ylab = "TPACK",
                 xlab = "Gender",
                 col = viridis(2), # c("pink", "blue"),
                 trace.label = "Target grade level")
```

Not so clear interaction effect, similar slopes? They do cross eventually.

```{r TPACK_gender_semester}
# https://www.statology.org/interaction-plot-r/
interaction.plot(x.factor = factor(data_clean$Gender),
                 trace.factor = factor(data_clean$semester),
                 response = data_clean$TPACK,
                 type = "b",
                 ylab = "TPACK",
                 xlab = "Gender",
                 col = viridis(2), # c("pink", "blue"),
                 trace.label = "Study year")
```

```{r TPACK_trinn_semester}
# https://www.statology.org/interaction-plot-r/
interaction.plot(x.factor = factor(data_clean$Trinn),
                 trace.factor = factor(data_clean$semester),
                 response = data_clean$TPACK,
                 type = "b",
                 ylab = "TPACK",
                 xlab = "Target grade level",
                 col = viridis(2), # c("pink", "blue"),
                 trace.label = "Study year")
```

### Level 2

```{r TPACK_semester_institute}
interaction.plot(x.factor = factor(data_clean$semester), # label=c("Year 2/3", "Year 5")),
                 trace.factor = factor(data_clean$studiested), # label=c("institute 1", "institute 2", "institute 3", "institute 4", "institute 5")),
                 response = data_clean$TPACK,
                 type = "b",
                 ylab = "TPACK",
                 xlab = "Year of study",
                 col = viridis(5), # c("red", "green", "orange", "pink", "blue"),
                 trace.label = "Institute")
```

A clear interaction effect between institute and semester on TPACK.

```{r TPACK_trinn_institute}
interaction.plot(x.factor = factor(data_clean$Trinn), # label=c("Year 2/3", "Year 5")),
                 trace.factor = factor(data_clean$studiested), # label=c("institute 1", "institute 2", "institute 3", "institute 4", "institute 5")),
                 response = data_clean$TPACK,
                 type = "b",
                 ylab = "TPACK",
                 xlab = "Year of study",
                 col = viridis(5), # c("red", "green", "orange", "pink", "blue"),
                 trace.label = "Institute")
```

```{r TPACK_gender_institute}
interaction.plot(x.factor = factor(data_clean$Gender),
                 trace.factor = factor(data_clean$studiested), #label=c("institute 1", "institute 2", "institute 3", "institute 4", "institute 5")),
                 response = data_clean$TPACK,
                 type = "b",
                 ylab = "TPACK",
                 xlab = "Gender",
                 col = viridis(5), #c("red", "green", "orange", "pink", "blue"),
                 trace.label = "Institute")
```

Not so clear interaction on TPACK from gender and institute.

@@

### Level 1

```{r level1}
# kovariater; we use scale to standardize when using interaction effects
# sjekk: er det riktig å skalere?
m1 <- lm_robust(scale(TPACK, center=T, scale=T) ~ factor(Gender) * (factor(Trinn) + factor(semester)), 
                clusters = factor(studiested), data=data_clean)
summary(m1)
```

### Level 2

```{r level2}
# studiested; HVL velges som referansekategori siden den har lavest TPACK-verdi av alle
m2 <- lm_robust(scale(TPACK) ~ factor(Gender) * (factor(Trinn) + factor(semester)) +        # level 1
                               factor(studiested) * (factor(semester) + factor(Gender)),    # level 2
                clusters = factor(studiested), data=data_clean)
summary(m2)
```

@@

### PCK

```{r PCK}
# PCK
m3 <- lm_robust(TPACK ~ factor(Gender) * (factor(Trinn) + factor(semester)) +         # level 1
                        factor(studiested) * (factor(semester) + factor(Gender)) +    # level 2
                        PCK, 
                clusters = factor(studiested), data=data_clean)
summary(m3)

@@

### TK

```{r TK}
# TK
m4 <- lm_robust(TPACK ~ factor(Gender) * (factor(Trinn) + factor(semester)) +        # level 1
                        factor(studiested) * (factor(semester) + factor(Gender))     # level 2
                        + PCK + TK, 
                clusters = factor(studiested), data=data_clean)
summary(m4)
